### 2024-07-26 README.Rmd
Update README to include cran instructions

<!-- badges: start -->
[![R-CMD-check](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/njtierney/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/njtierney/conmat?branch=master)
<!-- badges: end -->

@@

@@

```r
install.packages("conmat", repos = "https://njtierney.r-universe.dev")
```

@@

``` r
# install.packages("remotes")
remotes::install_github("njtierney/conmat")
```

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/idem-lab/conmat?branch=master)
<!-- badges: end -->

@@

You can install the stable version from cran with:

```r
install.packages("conmat")
```

@@

```r
install.packages("conmat", repos = "https://idem-lab.r-universe.dev")
```

@@

``` r
# install.packages("remotes")
remotes::install_github("idem-lab/conmat")
```
